The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-20 analysis/paper/paper.qmd

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                         # Managing paths
  "tidyverse",                    # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm",  # Text processing and analysis
  "tidygeocoder",                 # Working with spatial data
  "igraph", "ggraph"              # Network analysis and visualsation
)

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                                      # Managing paths
  "tidyverse",                                 # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm","topicmodels"  # Text processing and analysis
  "tidygeocoder",                              # Working with spatial data
  "igraph", "ggraph"                           # Network analysis and visualsation
)
